\documentclass{book}
\usepackage{xcolor}
\usepackage{tcolorbox}
\usepackage{fontspec}
\usepackage{hyphenat}
\usepackage[a5paper, total={5in, 6in}]{geometry}


% Set up the font using file paths
\setmainfont{Helvetica Neue}[
    Extension = .otf,
    UprightFont = HelveticaNeue-Regular,
    BoldFont = HelveticaNeue-Bold,
    ItalicFont = HelveticaNeue-RegularItalic,
    Path = /Users/conallmcginty/Downloads/helvetica-neue-master/
]

% Define colors
\definecolor{bluebubble}{RGB}{0,122,255}
\definecolor{greybubble}{RGB}{229,229,234}

% Create chat bubble environments
\newenvironment{chatbubble}[2]{%
    \par\noindent

    \def\content{#1}
    \settowidth{\mylen}{\content}

    \ifdim\mylen<.8\textwidth

    \else
    \begin{tcolorbox}[
        arc=2mm,
        boxrule=0pt,
        boxsep=0pt,
        left=2mm,
        right=2mm,
        top=2mm,
        bottom=2mm,
        colback=#1,
        coltext=#2,
        width=0.7\textwidth,
        before=\ifstrequal{#1}{bluebubble}{\hfill}{},
    ]
}{%
    \end{tcolorbox}
    \vspace{-1mm}
}

% Define character dialogues
\newcommand{\characterOne}[1]{%
    \begin{chatbubble}{bluebubble}{white}
        #1
    \end{chatbubble}
}

\newcommand{\characterTwo}[1]{%
    \begin{chatbubble}{greybubble}{black}
        #1
    \end{chatbubble}
}

\begin{document}

\nohyphens{

\characterOne{Hey there! How's it going?}

\characterTwo{Hi! I'm doing well, thanks for asking. How about you?}

\characterOne{I'm great! Just working on this LateX book that I'm making for Zoë.}

\characterTwo{Well THAT sounds fun. Are you going to show updates to your bezzie Steve?}

\characterOne{Ofc ofc ofc. I'm sure he'll probably get bored by the end of it. All these screenshots of pdf files. He ain't got time for that you know?}

\characterTwo{Well I'm sure he'll be happy to provide some constructive feedback. Steve is a man of opinions}

\characterOne{This is very true, this is very true.}

}

\end{document}
